---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# regweight

<!-- badges: start -->
[![codecov](https://codecov.io/gh/ddimmery/regweight/branch/main/graph/badge.svg?token=OG7J5YE3JB)](https://app.codecov.io/gh/ddimmery/regweight)
[![R-CMD-check](https://github.com/ddimmery/regweight/actions/workflows/r-cmd-check.yaml/badge.svg)](https://github.com/ddimmery/regweight/actions/workflows/r-cmd-check.yaml)
[![lint](https://github.com/ddimmery/regweight/actions/workflows/lint.yaml/badge.svg)](https://github.com/ddimmery/regweight/actions/workflows/lint.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/regweight)](https://CRAN.R-project.org/package=regweight)
<!-- badges: end -->

The goal of regweight is to make it easy to diagnose a model using [Aronow and Samii (2015)](https://onlinelibrary.wiley.com/doi/abs/10.1111/ajps.12185) regression weights.

In short, these weights show which observations are most influential for determining the observed value of a coefficient in a linear regression. If the linear regression is aiming to estimate causal effects, this implies that the OLS *estimand* may differ from the average treatment effect. These linear regression weights provide, in some sense, the most precise estimate available given a conditioning set (and a linear model). These weights are in expectation the conditional variance of the variable of interest (given the other covariates in the model).

For more details, see `vignette("example-usage")`.

## Installation

You can install regweight like so:

```{r eval = FALSE}
# From CRAN:
install.packages("regweight")

# Or the development version from GitHub:
# install.packages("devtools")
devtools::install_github("ddimmery/regweight")
```

## Example

This is a basic example which shows you how to analyze the implicit regression weights in a simple problem:

```{r setup}
library(regweight)
library(estimatr)
data(penguins, package = "palmerpenguins")

model <- lm_robust(body_mass_g ~ ., penguins)
summary(model)
```

Let's say that we want to explore the effect of `flipper_length_mm` on `body_mass_g`. Which units have high implicit weight in estimating this effect?

It's very easy to use `regweight` to answer this question:

```{r regweight}
rw_model <- calculate_weights(model, "flipper_length_mm")
hist(rw_model)
```

We can see how the distribution of weights over islands varies:
```{r discrete}
plot(rw_model, penguins$island)
```

We can similarly see the implicit distribution of `bill_length_mm` in the nominal (unweighted) and implicit (regression weighted) sample:

```{r cts}
plot(rw_model, penguins$bill_length_mm)
```

Or get a table of summary statistics:

```{r summ}
summary(
  rw_model,
  dplyr::select(penguins, island, bill_length_mm),
  output = "html"
)
```
